Towards a Cognitive System That Can Recognize Spatial Regions Based on Context

### 2012-01-24 scenarios/cdsr/trunk/papers/AAAI2012/evaluation.tex
editing eval section

To evaluate our progress toward building a cognitive system capable of reasoning about these CDSRs, we conducted the an experiment focusing on the following questions:
\begin{itemize}
\item{Can anchor points capture context-dependent spatial regions?}
\item{When provided with a base representation containing a labelled CDSR, how well does our approach identify the CDSR in a given target?}
\end{itemize}

@@

To determine how people define CDRSs, we asked three users to draw polygons for each region type for each room. This task was performed using a webpage (link removed for blind review) shown in the inset in Figure~\ref{fig:ug40} on which each user was presented with an image of the real room plus the map data generated by the robot (as in Figure~\ref{fig:rooms}) onto which the drawing could be done. We call the each user-defined polygon a \textit{target region} against which we evaluate our transfers.

@@

We compare the transfer results against our manually encoded CDSRs for the target region and against a region that represents the entire room. Results on the entire room provide a baseline performance measure. The performance of the manually encoded CDSRs evaluates how well the anchor points capture the user defined regions and provides a ceiling for the inferred region's performance.

\subsection{Results}
\begin{table}
\small
\caption{Overall Performance}
  \label{tab:overall}	
\begin{tabular}{|c|c|c|}
\hline
Inferred & Manually Encoded & Entire Room \\
\hline
$\bar{p}$=.45 $\sigma$=.37, $\bar{r}$=.45 $\sigma$=.38 & $\bar{p}$=.71 $\sigma$=.29, $\bar{r}$=.66 $\sigma$=.24  & $\bar{p}$=.17 $\sigma$=.11, $\bar{r}$=.98 $\sigma$=.05  \\
\hline
\end{tabular}
\end{table}

@@

\begin{table}
\small
\caption{Performance by Region Type}
  \label{tab:region}	
\begin{tabular}{|c|c|c|c|}
\hline
Region & Inferred & Manually Encoded & Entire Room \\
\hline
Front & $\bar{p}$=.33 $\sigma$=.34, $\bar{r}$=.52 $\sigma$=.40 & $\bar{p}$=.60 $\sigma$=.29, $\bar{r}$=.82 $\sigma$=.19  & $\bar{p}$=.15 $\sigma$=.09, $\bar{r}$=1 $\sigma$=0  \\
\hline
Back & $\bar{p}$=.45 $\sigma$=.35, $\bar{r}$=.56 $\sigma$=.40 & $\bar{p}$=.66 $\sigma$=.25, $\bar{r}$=.84 $\sigma$=.17  & $\bar{p}$=.11 $\sigma$=.06, $\bar{r}$=.99 $\sigma$=.03  \\
\hline
Front Rows & $\bar{p}$=.62 $\sigma$=.36, $\bar{r}$=.22 $\sigma$=.21 & $\bar{p}$=.82 $\sigma$=.30, $\bar{r}$=.50 $\sigma$=.11  & $\bar{p}$=.22 $\sigma$=.08, $\bar{r}$=1 $\sigma$=0  \\
\hline
Back Rows & $\bar{p}$=.74 $\sigma$=.28, $\bar{r}$=.43 $\sigma$=.23 & $\bar{p}$=.80 $\sigma$=.29, $\bar{r}$=.43 $\sigma$=.26  & $\bar{p}$=.19 $\sigma$=.06, $\bar{r}$=1 $\sigma$=0  \\
\hline
Kitchen & $\bar{p}$=.23 $\sigma$=.03, $\bar{r}$=.09 $\sigma$=.02 & $\bar{p}$=.78 $\sigma$=.20, $\bar{r}$=.71 $\sigma$=.13  & $\bar{p}$=.16 $\sigma$=.02, $\bar{r}$=.92 $\sigma$=.13  \\
\hline
Office & $\bar{p}$=.05 $\sigma$=.01, $\bar{r}$=.06 $\sigma$=.06 & $\bar{p}$=.78 $\sigma$=.29, $\bar{r}$=.55 $\sigma$=.20  & $\bar{p}$=.08 $\sigma$=.03, $\bar{r}$=.93 $\sigma$=.06  \\
Living Room & $\bar{p}$=0 $\sigma$=0, $\bar{r}$=0 $\sigma$=0 & $\bar{p}$=.63 $\sigma$=.34, $\bar{r}$=.54 $\sigma$=.13  & $\bar{p}$=.35 $\sigma$=.22, $\bar{r}$=.96 $\sigma$=.06  \\
\hline
\end{tabular}
\end{table}

>>>>

To evaluate our progress toward building a cognitive system capable of reasoning about CDSRs, we conducted the an experiment focusing on the following questions:
\begin{itemize}
\item{Are anchor points able to encode context-dependent spatial regions?}
\item{When provided with a base representation containing a labelled CDSR, how well does our approach identify the CDSR in a given target?}
\end{itemize}

@@

To determine how people define CDRSs, we asked three na\"ive users to draw polygons for each region type for each room. This task was performed using a webpage (link removed for blind review) shown in the inset in Figure~\ref{fig:ug40} on which each user was presented with an image of the real room plus the map data generated by the robot (as in Figure~\ref{fig:rooms}) onto which the drawing could be done. The user-defined polygons define the \textit{target regions} against which we evaluate our transfers.

@@

Using this approach we generate results showing the matches between each of the following pairs of regions: the transferred region and the appropriate target region; the manually annotated CDSR in the target and appropriate target region; and the region for the whole room and the target region. 
 Results comparing transferred and target regions measure how well the output of our system matches user expectations. Results comparing the manual annotations to the target regions measure how well the anchor point-based regions we chose match the users' regions (who were not constrained to anchor points). Results comparing whole rooms to target regions provide a baseline performance for comparison.

\subsection{Results}
\begin{table}
\small
\begin{tabular}{|c|c|c|}
\hline
Inferred & Manually Encoded & Entire Room \\
\hline
$\bar{p}$=.45 $\sigma$=.37, $\bar{r}$=.45 $\sigma$=.38 & $\bar{p}$=.71 $\sigma$=.29, $\bar{r}$=.66 $\sigma$=.24  & $\bar{p}$=.17 $\sigma$=.11, $\bar{r}$=.98 $\sigma$=.05  \\
\hline
\end{tabular}
\caption{Overall Performance}
  \label{tab:overall}

\end{table}

@@

\begin{table}
\small
\begin{tabular}{|c|c|c|c|}
\hline
Region & Inferred & Manually Encoded & Entire Room \\
\hline
Front & $\bar{p}$=.33 $\sigma$=.34, $\bar{r}$=.52 $\sigma$=.40 & $\bar{p}$=.60 $\sigma$=.29, $\bar{r}$=.82 $\sigma$=.19  & $\bar{p}$=.15 $\sigma$=.09, $\bar{r}$=1 $\sigma$=0  \\
\hline
Back & $\bar{p}$=.45 $\sigma$=.35, $\bar{r}$=.56 $\sigma$=.40 & $\bar{p}$=.66 $\sigma$=.25, $\bar{r}$=.84 $\sigma$=.17  & $\bar{p}$=.11 $\sigma$=.06, $\bar{r}$=.99 $\sigma$=.03  \\
\hline
Front Rows & $\bar{p}$=.62 $\sigma$=.36, $\bar{r}$=.22 $\sigma$=.21 & $\bar{p}$=.82 $\sigma$=.30, $\bar{r}$=.50 $\sigma$=.11  & $\bar{p}$=.22 $\sigma$=.08, $\bar{r}$=1 $\sigma$=0  \\
\hline
Back Rows & $\bar{p}$=.74 $\sigma$=.28, $\bar{r}$=.43 $\sigma$=.23 & $\bar{p}$=.80 $\sigma$=.29, $\bar{r}$=.43 $\sigma$=.26  & $\bar{p}$=.19 $\sigma$=.06, $\bar{r}$=1 $\sigma$=0  \\
\hline
Kitchen & $\bar{p}$=.23 $\sigma$=.03, $\bar{r}$=.09 $\sigma$=.02 & $\bar{p}$=.78 $\sigma$=.20, $\bar{r}$=.71 $\sigma$=.13  & $\bar{p}$=.16 $\sigma$=.02, $\bar{r}$=.92 $\sigma$=.13  \\
\hline
Office & $\bar{p}$=.05 $\sigma$=.01, $\bar{r}$=.06 $\sigma$=.06 & $\bar{p}$=.78 $\sigma$=.29, $\bar{r}$=.55 $\sigma$=.20  & $\bar{p}$=.08 $\sigma$=.03, $\bar{r}$=.93 $\sigma$=.06  \\
\hline
Living Room & $\bar{p}$=0 $\sigma$=0, $\bar{r}$=0 $\sigma$=0 & $\bar{p}$=.63 $\sigma$=.34, $\bar{r}$=.54 $\sigma$=.13  & $\bar{p}$=.35 $\sigma$=.22, $\bar{r}$=.96 $\sigma$=.06  \\
\hline
\end{tabular}
\caption{Performance by Region Type}
  \label{tab:region}	
\end{table}
